Dragonfly Territory Ananlysis

### 2020-11-25 analysis/analysisSS.Rmd
working on plots

iElegansSAY <- dplyr::rename(iElegansAY, iElegans_abundance = ABUNDANCE)
cPuellaSAY <- dplyr::rename(cPuellaAY, cPuella_abundance = ABUNDANCE)
lSponsaSAY <- dplyr::rename(lSponsaAY, lSponsa_abundance = ABUNDANCE)
lQuadrimaculataSAY <- dplyr::rename(lQuadrimaculataAY, lQuadrimaculata_abundance = ABUNDANCE)
sStriolatumSAY <- dplyr::rename(sStriolatumAY, sStriolatum_abundance = ABUNDANCE)

@@

abundanceSums <- data.frame(rowSums(fullAbundanceDF[,c(2,3,4,5,6,7,8,9,10,11)]))

>>>>

iElegansSAY <- dplyr::rename(iElegansAY, iElegansAbundance = ABUNDANCE)
cPuellaSAY <- dplyr::rename(cPuellaAY, cPuellaAbundance = ABUNDANCE)
lSponsaSAY <- dplyr::rename(lSponsaAY, lSponsaAbundance = ABUNDANCE)
lQuadrimaculataSAY <- dplyr::rename(lQuadrimaculataAY, lQuadrimaculataAbundance = ABUNDANCE)
sStriolatumSAY <- dplyr::rename(sStriolatumAY, sStriolatumAbundance = ABUNDANCE)

@@

abundanceSums <- data.frame(rowSums(fullAbundanceDF[,c(2,3,4,5,6,7,8,9,10,11)]))
abundance_year <- cbind(abundanceSums, new_col = YEAR)
abundanceYearSums <- subset(abundance_year, select = c(2,1))

abunYearSums_1 <- dplyr::rename(abundanceYearSums, year = new_col)
abunYearsSums <- dplyr::rename(abunYearSums_1, total_abundance = rowSums.fullAbundanceDF...c.2..3..4..5..6..7..8..9..10..11...)

plot(abunYearsSums$year, abunYearsSums$total_abundance)

# I want plots for all 10 species

par(mfrow=c(2,5))
plot(bPratenseCompAY$YEAR, bPratenseCompAY$bPratenseAbundance, main = "Brachytron pratense", xlab = "Year", ylab = "Abundance")
plot(pNymphulaCompAY$YEAR, pNymphulaCompAY$pNymphulaAbundance, main = "Pyrrhosa nymphula", xlab = "Year", ylab = "Abundance")
plot(aCyaneaCompAY$YEAR, aCyaneaCompAY$aCyaneaAbundance, main = "Aeshna cyanea", xlab = "Year", ylab = "Abundance")
plot(sSanguineumCompAY$YEAR, sSanguineumCompAY$sSanguineumAbundance, main = "Sympetrum sanguineum", xlab = "Year", ylab = "Abundance")
plot(aGrandisCompAY$YEAR, aGrandisCompAY$aGrandisAbundance, main = "Aeshna grandis", xlab = "Year", ylab = "Abundance")
plot(cPuellaCompAY$YEAR, cPuellaCompAY$cPuellaAbundance, main = "Coenagrion puella", xlab = "Year", ylab = "Abundance")
plot(iElegansCompAY$YEAR, iElegansCompAY$iElegansAbundance, main = "Ischnura elegans", xlab = "Year", ylab = "Abundance")
plot(lSponsaCompAY$YEAR, lSponsaCompAY$lSponsaAbundance, main = "Lestes sponsa", xlab = "Year", ylab = "Abundance")
plot(lQuadrimaculataCompAY$YEAR, lQuadrimaculataCompAY$lQuadrimaculataAbundance, main = "Libellula quadrimaculata", xlab = "Year", ylab = "Abundance")
plot(sStriolatumCompAY$YEAR, sStriolatumCompAY$sStriolatumAbundance, main = "Sympetrum striolatum", xlab = "Year", ylab = "Abundance")

# read in Odonate names, this is a .csv in the github repo

odonata_names <- read.csv("~/GitHub/rrirfinalproject/odonata_names.csv")
